Contribution Title\thanks{Supported by organization x.}

### 2019-12-10 sections/evaluation.tex
add some new results from i-uip-pure, it did almost too well

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm} | m{2cm} | m{2.5cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Cl Reduction\% \\ 
\hline
$\MapleBase$ & 221 & 5018.89 & 62.6 & 36.53\% \\ 
\hline
$\MapleIUIPPURE$ & 226 & 4920.04 & 49.6 & 41.6\% \\ 
\hline
$\MapleIUIMIN$ & 226 & 4890.67 & 45.2 & 47.8\%  (51.19\%)\\ 
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of $\MapleBase$ , $\MapleIUIPPURE$  and $\MapleIUIMIN$ on SAT2019 race main track.
CL Reduction\% is the clause size reduction ratio comparing to non-minimized 1-UIP clauses, and the values in the brackets are the non-cumulative reduction ratio.}
\label{fig:t1}
\end{figure}

Fig.~\ref{fig:t1} shows that both version of $\IUIP$ solved five more instances than the baseline solver with lower PAR-2 scores. $\IUIPMIN$ has marginally lower PAR-2 score than $\IUIPPURE$. Both $\IUIPPURE$ and $\IUIPMIN$ produce clause with significantly smaller size than 1-UIP by 27.7\% and 20.7\%, respectively. Fig.~\ref{fig:len_pdf} shows the probability density distribution (PDF) of the average clause length reduction of $\IUIPMIN$ relative to 1-UIP. $\IUIPMIN$ learning produces shorter clauses for 88.25\% instances, and average relative reduction from 1-UIP is 18.685\%. Fig.~\ref{fig:len_compare} compares the absolute average clause size from $\IUIPMIN$ and 1-UIP, and it shows that $\IUIPMIN$ in general produces smaller clauses, and the size reduction is more significant for instances with large average 1-UIP clause size.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{clause_length_PDF.png}
    \caption{Average clause (relative to 1-UIP clauses) size distribution. X axis indicates the relative size difference, and Y axis indicates the PDF.}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{i-uip-sizes-compare.png}
    \caption{Average clause size comparison plot. Each point in the plot represents an benchmark instance. X and Y axis shows the clause length from $\IUIP$ and 1-UIP, respectively. Each green (red) dot represents an compared instance between $\MapleBase$ and $\MapleIUIMIN$ ($\IUIPPURE$).   }
    \label{fig:len_compare}
\end{figure}

@@

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.5cm} | m{4cm}| m{2cm} | m{2.75cm} |  } 
\hline
Solver & \# solved (SAT, UNSAT) & PAR-2 & Avg clause Size \\ 
\hline
1-UIP & 221 (132, 89)  & 5018.89 & 62.6  \\ 
\hline
i-UIP & \textbf{226} (135, \textbf{91}) & 4890.67 & 45.2 \\ 
\hline
i-UIP-greedy & \textbf{226} (135, \textbf{91})  & \textbf{4866.94} & 47.7 \\
\hline
i-UIP-active-Inclusive & 225 (\textbf{138}, 87) & 4958.49 & 52..12 \\
\hline
i-UIP-active-Exclusive & 223 (134, 89) & 5015.23 & \textbf{43.2} \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of 1-UIP ($\MapleBase$), i-UIP($\IUIPMIN$), i-UIP-Greedy,
i-UIP-Inclusive, and i-UIP-Exclusive on SAT2019 race main track.}
\label{fig:t4}
\end{figure}

@@

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.7cm} | m{4cm}| m{2cm} | m{2.75cm} |  } 
\hline
Solver & \# solved (SAT, UNSAT) & PAR-2 & Avg clause Size \\ 
\hline
$\MapleSeven$ & 232 (135, 97)  & 4755.96 & 61.9  \\ 
\hline
$\MapleSeven$-i-uip & \textbf{240} (\textbf{144}, 96) & \textbf{4601.25} & \textbf{36.97} \\ 
\hline
$\MapleSeven$-i-greedy & 237 (140, \textbf{97}) & 4678.434 & 43.62 \\ 
\hline
$\MapleSeven$-i-inclusive & 234 (137, 97) & 4718.03 & 37.96 \\ 
\hline
\hline
$\expSATShort$ & 237 (137, 100)  & 4628.96 & 63.19 \\
\hline
$\expSATShort$-i-uip & 241 (143, 98) & 4524.28 & 46.29 \\ 
\hline
$\expSATShort$-i-greedy & 244 (143, \textbf{101}) & \textbf{4460.92} & 47.25 \\
\hline
$\expSATShort$-i-inclusive & \textbf{245} (\textbf{146}, 99) & 4475.76 & \textbf{45.33} \\
\hline
\hline
$\MapleNineShort$ & 243 (145, \textbf{98}) & 4450.24 & 61.00 \\
\hline
$\MapleNineShort$-i-uip & 244 (148, 96) & \textbf{4409.88} & \textbf{37.43} \\
\hline
$\MapleNineShort$-i-greedy & 243 (146, 97) & 4476.73 & 40.65 \\
\hline
$\MapleNineShort$-i-inclusive & \textbf{245} (\textbf{150}, 95) & 4425.99 & 37.60 \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of 1-UIP, i-UIP($\IUIPMIN$), i-UIP-Greedy,
i-UIP-Inclusive on SAT2019 race main track.}
\label{fig:t5}
\end{figure}

\nf{Benchmark results from running $\expSAT$ are harder to produce due to the randomness caused by the solver's strategy for selecting branching heuristics: the solver runs 2500s with LBR and the remaining 2500s with VSIDS. This is problematic for reproducing results because two runs of the same solver can be in different states at 2500s mark, and switching heuristics at different states will cause further divergence. The divergence can be quiet impactful (+- 2 instances at most for i-uip-active). For reproducible benchmark results, should we turn off the 2500s heuristic switching? Should we add a new section for the reproducible result? or remove the existing ones?}

Table~\ref{fig:t5} shows the benchmark result of $\IUIP$ configurations on different solvers. All three configurations of $\IUIP$ outperformed 1-UIP on $\MapleSeven$. i-UIP, i-UIP-Greedy and i-UIP-inclusive solved 8, 5 and 2 more instances, respectively, whiling producing smaller clauses.  The improvement of $\IUIP$ is more significant on $\MapleSeven$ than on $\MapleBase$ for both solved instances and clause size reduction. This may suggests that $\IUIP$ and the recent learnt clause minimization approach~\cite{} synergies well because: 1) i-UIP clauses are shorter with more common literals which allows vivification~\cite{} to prune literals more aggressively through unit propagation. 2) using $\IUIP$ instead of 1-UIP scheme to analyze conflicts during vivification could derive shorter clauses.

>>>>

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.3cm} | m{2cm}| m{2cm} | m{2cm} | m{2.7cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Cl Reduction\% \\ 
\hline
$\MapleBase$ & 221 (132, 89) & 5018.89 & 62.6 & 36.53\% \\ 
\hline
$\MapleIUIPPURE$ & \textbf{228} (135, 93) & \nf{4867.37} & 49.88 & 41.6\%  (42.72\%)\\ 
\hline
$\MapleIUIMIN$ & 226 (135, 91) & 4890.67 & \textbf{45.2} & \textbf{47.8\% (51.19\%)}\\ 
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of $\MapleBase$ , $\MapleIUIPPURE$  and $\MapleIUIMIN$ on SAT2019 race main track.
CL Reduction\% is the clause size reduction ratio comparing to non-minimized 1-UIP clauses, and the values in the brackets are the non-cumulative reduction ratio.}
\label{fig:t1}
\end{figure}

Fig.~\ref{fig:t1} shows that both version of $\IUIP$ solved five more instances than the baseline solver with lower PAR-2 scores. $\IUIPMIN$ has marginally lower PAR-2 score than $\IUIPPURE$. Both $\IUIPPURE$ and $\IUIPMIN$ produce clause with significantly smaller size than 1-UIP by 27.7\% and 20.7\%, respectively. Fig.~\ref{fig:len_pdf} shows the probability density distribution (PDF) of the average clause length reduction of $\IUIPMIN$ relative to 1-UIP. $\IUIPMIN$ learning produces shorter clauses for 88.25\% instances, and average relative reduction from 1-UIP is 18.685\%. Fig.~\ref{fig:len_compare} compares the absolute average clause size from $\IUIPMIN$ and 1-UIP, and it shows that $\IUIPMIN$ in general produces smaller clauses, and the size reduction is more significant for instances with large average 1-UIP clause size. 
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{figures/factor_clause_length_PDF.png}
    \caption{ Relative Clause size distribution. X axis indicates the relative size of i-uip clause (with respect to 1-uip clause) for each instance, and Y axis indicates the probability density.}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{i-uip-sizes-compare.png}
    \caption{Average clause size comparison plot. Each point in the plot represents an instance. X and Y axis shows the clause length from $\IUIP$ and 1-UIP, respectively. Each green (red) dot represents an compared instance between $\MapleBase$ and $\MapleIUIMIN$ ($\IUIPPURE$).   }
    \label{fig:len_compare}
\end{figure}

@@

@@

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.5cm} | m{4cm}| m{2cm} | m{2.75cm} |  } 
\hline
Solver & \# solved (SAT, UNSAT) & PAR-2 & Avg clause Size \\ 
\hline
1-UIP & 221 (132, 89)  & 5018.89 & 62.6  \\ 
\hline
\nf{i-UIP-PURE} &\textbf{228} (135, \nf{93}) & 4867.37 & 49.88 \\
\hline
i-UIP & 226 (135, 91) & 4890.67 & 45.2 \\ 
\hline
i-UIP-greedy & 226 (135, 91)  & \textbf{4866.94} & 47.7 \\
\hline
i-UIP-active-Inclusive & 225 (\textbf{138}, 87) & 4958.49 & 52..12 \\
\hline
i-UIP-active-Exclusive & 223 (134, 89) & 5015.23 & \textbf{43.2} \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of 1-UIP ($\MapleBase$),i-UIP-PURE, i-UIP($\IUIPMIN$), i-UIP-Greedy,
i-UIP-Inclusive, and i-UIP-Exclusive on SAT2019 race main track.}
\label{fig:t4}
\end{figure}

@@

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.7cm} | m{4cm}| m{2cm} | m{2.75cm} |  } 
\hline
Solver & \# solved (SAT, UNSAT) & PAR-2 & Avg clause Size \\ 
\hline
$\MapleSeven$ & 232 (135, 97)  & 4755.96 & 61.9  \\ 
\hline
$\MapleSeven$-i-uip & 240 (144, 96) & 4601.25 & \textbf{36.97} \\ 
\hline
$\MapleSeven$-i-greedy & 237 (140, 97) & 4678.434 & 43.62 \\ 
\hline
$\MapleSeven$-i-inclusive & 234 (137, 97) & 4718.03 & 37.96 \\
\hline
$\MapleSeven$-i-pure & 245 (146, \nf{99}) & \nf{4488.30} & 43.76 \\
\hline
\hline
$\expSATShort$ & 237 (137, 100)  & 4628.96 & 63.19 \\
\hline
$\expSATShort$-i-uip & 241 (143, 98) & 4524.28 & 46.29 \\ 
\hline
$\expSATShort$-i-greedy & 244 (143, \textbf{101}) & \textbf{4460.92} & 47.25 \\
\hline
$\expSATShort$-i-inclusive & \textbf{245} (\textbf{146}, 99) & 4475.76 & \textbf{45.33} \\
\hline
\hline
$\MapleNineShort$ & 243 (145, \textbf{98}) & 4450.24 & 61.00 \\
\hline
$\MapleNineShort$-i-uip & 244 (148, 96) & \textbf{4409.88} & \textbf{37.43} \\
\hline
$\MapleNineShort$-i-greedy & 243 (146, 97) & 4476.73 & 40.65 \\
\hline
$\MapleNineShort$-i-inclusive & \textbf{245} (\textbf{150}, 95) & 4425.99 & 37.60 \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of 1-UIP, i-UIP($\IUIPMIN$), i-UIP-Greedy,
i-UIP-Inclusive on SAT2019 race main track.}
\label{fig:t5}
\end{figure}

\nf{Benchmark results from running $\expSAT$ are harder to produce due to the randomness caused by the solver's strategy for selecting branching heuristics: the solver runs 2500s with LBR and the remaining 2500s with VSIDS. This is problematic for reproducing results because two runs of the same solver can be in different states at 2500s mark, and switching heuristics at different states will cause further divergence. The result can be quiet impactful (+- 2 instances at most for i-uip-active). For reproducible benchmark results, should we turn off the 2500s heuristic switching? Should we add a new section for the reproducible result? or remove the existing ones?}

Table~\ref{fig:t5} shows the benchmark result of $\IUIP$ configurations on different solvers. All three configurations of $\IUIP$ outperformed 1-UIP on $\MapleSeven$. i-UIP, i-UIP-Greedy and i-UIP-inclusive solved 8, 5 and 2 more instances, respectively, whiling producing smaller clauses.  The improvement of $\IUIP$ is more significant on $\MapleSeven$ than on $\MapleBase$ for both solved instances and clause size reduction. This may suggests that $\IUIP$ and the recent learnt clause minimization approach~\cite{} synergies well because i-UIP clauses are shorter with more common literals which allows vivification~\cite{} to prune literals more aggressively through more unit propagation.
